\chapter{Exporting}
\label{export}
\index{exporting}

\section{Overview}

Publication records may be exported from the system using the \emp{export} command
(here to a file in PDF format):
\begin{code}
# publish export outputfile.pdf
\end{code}

One or more filters may also be specified to extract only papers
matching (or not matching) a number of attributes, for example:
\begin{code}
# publish export year=2008 category=talks \
  author=langtangen outputfile.pdf
\end{code}

During export, all papers are read from the database
(\emp{papers.pub}), validated, filtered, and then formatted in the
desired output format as determined by the filename suffix (see
Figure~\ref{fig:export}).

\section{Supported File Formats}

\package{} currently exports to the following file formats:
\begin{itemize}
  \item
    \emp{pub}
  \item
    BibTeX
  \item
    \LaTeX
  \item
    PDF
\end{itemize}

The \LaTeX format may be useful for generating publication records
for inclusion in a CV or an annual report.

\section{Filtering}
\index{filter}

Filters may be specified in one of two ways. Either, one may
specify an attribute that must be satisfied by all papers to be
exported, or one may specify an attribute that \emph{must not} be
satisfied by the papers to be exported. It is also possible to list
several attributes and mix the two types of filters. The exported
papers must then satisfy each one of the listed filters.

The following example demonstrates how to export all journal papers
from the year 2008 which are \emph{not} written by H. P. Langtangen:
\begin{code}
# publish export year=2008 category=articles \
  author!="H. P. Langtangen" papers.pdf
\end{code} 

When filtering on author names, it is possible to either list only the
author's last name, the name with initials, or the full name. Thus,
the following examples are all valid, but they may or may not give the
same result, depending on how many authors are named ``Langtangen'',
whether or not papers have been entered only with initials or with
full names:
\begin{code}
# publish export author=langtangen papers.pdf
# publish export author="H. P. Langtangen" papers.pdf
# publish export author="Hans Petter Langtangen" papers.pdf
\end{code}
In all of these examples, the filter will match all papers where the
given author name matches at least one author in the author list (for
papers with more than one author).

\section{Options}
\index{PDF viewer}

The following additional options may be given to the \emp{export} command:
\begin{itemize}
\item
  \emp{view\_pdf=no} \\

  Don't display generated PDF files when exporting to PDF.
\item
  \emp{pdf\_viewer=<command>} \\

  Specify command that should be used to display PDF files.
\end{itemize}
