\chapter{Internal Format (\texttt{.pub})}
\label{pubformat}

\section{Overview}

Papers are stored in the \emp{pub} format according to the following scheme:
\begin{code}
* category
** title
   attribute: value
   attribute: value
   ...
** title
   attribute: value
   attribute: value
   ...
* category
   ...
\end{code}

Each category is specified by a \emp{*} followed by a single space and
the name of the category.  Within each category, each paper is
specified by \emp{**} followed by a single space and the title of the
paper. Then follows for each paper all attribute-value pairs separated
by \emp{:} (spaces ignored).

Each category specifies a number of required attributes that must be
specified for each paper within that category. In addition to the
required attributes, any number of additional attributes may be
specified.

Currently, all attribute-value pairs must be entered in a single line
(multi-line values not supported).

\section{Example}

\tiny
\begin{code}
* articles
** Numerical Methods for Incompressible Viscous Flow
   author:    H. P. Langtangen, K.-A. Mardal, R. Winther
   journal:   Advances in Water Resources
   year:      2002
   status:    published
   number:    8
   pages:     1125--1146
   volume:    25
   key:       SC.4.Langtangen.2002.b
   entrytype: article
** Unified Framework for Finite Element Assembly
   author:    Martin Sandve Aln{\ae}s, Anders Logg, Kent-Andre Mardal, Ola Skavhaug, Hans Petter Langtangen
   journal:   International Journal of Nonlinear Modelling in Science and Engineering
   year:      2009
   status:    published
   entrytype: article
   key:       Simula.SC.96
* books
** Computational Partial Differential Equations - Numerical Methods and Diffpack Programming
   author:    H. P. Langtangen
   publisher: Springer-Verlag
   year:      2003
   status:    published
   note:      2nd edition, 855 pages
   key:       SC.1.Langtangen.2003
   entrytype: book
** {P}ython Scripting for Computational Science
   author:    Hans Petter Langtangen
   publisher: Springer-Verlag
   year:      2008
   status:    published
   isbn:      978-3-540-73915-9
   edition:   third
   duplicate: True
   key:       Simula.SC.63
   entrytype: book
   address:   Heidelberg
* theses
** Applications of High Level Software for Parallel Solution of Partial Differential Equations
   author:     {\AA}smund {\O}deg{\aa}rd
   school:     Department of Informatics, University of Oslo
   year:       2006
   thesistype: phd
   status:     published
   key:        Odegard.2006.1
   entrytype:  phdthesis
\end{code}
\normalsize

\section{Required Attributes}

\subsection{Category \emp{articles}}

This category is for refereed articles published in international
journals.

Required attributes are \emp{author}, \emp{title}, \emp{journal}, \emp{year}, and \emp{status}.

\subsection{Category \emp{books}}

This category is for books.

Required attributes are \emp{author}, \emp{title}, \emp{publisher}, \emp{year}, and \emp{status}.

\subsection{Category \emp{edited}}

This category is for edited books (where the authors are the editors of
the book).

Required attributes are \emp{author}, \emp{title}, \emp{publisher}, \emp{year}, and \emp{status}.

\subsection{Category \emp{chapters}}

This category is for parts of books, which may be a chapter, a
section, and/or a range of pages.

Required attributes are \emp{author}, \emp{title}, \emp{chapter}
and/or \emp{pages}, \emp{editor}, \emp{publisher}, \emp{year}, and
\emp{status}.

\subsection{Category \emp{refproceedings}}

This category is for \emph{refereed} articles in conference
proceedings.

Required attributes are \emp{author}, \emp{title}, \emp{booktitle},
\emp{year}, and \emp{status}.

\subsection{Category \emp{proceedings}}

This category is for articles in conference proceedings without
referee.

Required attributes are \emp{author}, \emp{title}, \emp{booktitle},
\emp{year}, and \emp{status}.

\subsection{Category \emp{reports}}

This category is for reports/preprints published by a school or other
institution, usually numbered within a series.

Required attributes are \emp{author}, \emp{title}, \emp{institution},
\emp{year}, and \emp{status}.

\subsection{Category \emp{manuals}}

This category is for technical documentation.

Required attributes are \emp{author}, \emp{title}, and \emp{status}.

\subsection{Category \emp{thesis}}

This category is for PhD, Licentiate, Diploma, or Master's theses.

Required attributes are \emp{author}, \emp{title}, \emp{school},
\emp{year}, \emp{thesistype}, and \emp{status}.

\subsection{Category \emp{courses}}

This category is for courses given at a university or other
educational institution.

Required attributes are \emp{author}, \emp{title}, \emp{code},
\emp{institution}, \emp{year}, and \emp{status}.

\subsection{Category \emp{talks}}

This category is for talks at meetings (conference or workshop).

Required attributes are \emp{author}, \emp{title}, \emp{meeting}, \emp{year}, and \emp{status}.

\subsection{Category \emp{misc}}

This category should be used when nothing else fits. Required attributes are
\emp{title} and \emp{status}.
