% This is the old version of Required Attributes. We now just refer
% to defaults.py for what they are.

\section{Required Attributes}

\subsection{Category \emp{articles}}

This category is for refereed articles published in international
journals.

Required attributes are \emp{author}, \emp{title}, \emp{journal}, \emp{year}, and \emp{status}.

\subsection{Category \emp{books}}

This category is for books.

Required attributes are \emp{author}, \emp{title}, \emp{publisher}, \emp{year}, and \emp{status}.

\subsection{Category \emp{edited}}

This category is for edited books (where the authors are the editors of
the book).

Required attributes are \emp{author}, \emp{title}, \emp{publisher}, \emp{year}, and \emp{status}.

\subsection{Category \emp{chapters}}

This category is for parts of books, which may be a chapter, a
section, and/or a range of pages.

Required attributes are \emp{author}, \emp{title}, \emp{chapter}
and/or \emp{pages}, \emp{editor}, \emp{publisher}, \emp{year}, and
\emp{status}.

\subsection{Category \emp{refproceedings}}

This category is for \emph{refereed} articles in conference
proceedings.

Required attributes are \emp{author}, \emp{title}, \emp{booktitle},
\emp{year}, and \emp{status}.

\subsection{Category \emp{proceedings}}

This category is for articles in conference proceedings without
referee.

Required attributes are \emp{author}, \emp{title}, \emp{booktitle},
\emp{year}, and \emp{status}.

\subsection{Category \emp{reports}}

This category is for reports/preprints published by a school or other
institution, usually numbered within a series.

Required attributes are \emp{author}, \emp{title}, \emp{institution},
\emp{year}, and \emp{status}.

\subsection{Category \emp{manuals}}

This category is for technical documentation.

Required attributes are \emp{author}, \emp{title}, and \emp{status}.

\subsection{Category \emp{thesis}}

This category is for PhD, Licentiate, Diploma, or Master's theses.

Required attributes are \emp{author}, \emp{title}, \emp{school},
\emp{year}, \emp{thesistype}, and \emp{status}.

\subsection{Category \emp{courses}}

This category is for courses given at a university or other
educational institution.

Required attributes are \emp{author}, \emp{title}, \emp{code},
\emp{institution}, \emp{year}, and \emp{status}.

\subsection{Category \emp{talks}}

This category is for talks at meetings (conference or workshop).

Required attributes are \emp{author}, \emp{title}, \emp{meeting}, \emp{year}, and \emp{status}.

\subsection{Category \emp{misc}}

This category should be used when nothing else fits. Required attributes are
\emp{title} and \emp{status}.
