\begin{enumerate}
\item
 ACM Transactions on Mathematical Software\\
 ACM Trans. Math. Software\\
 ISSN: 0098-3500
\item
 ACM Computing Surveys\\
 ACM Comput. Surv.\\
 ISSN: 0360-0300
\item
 ACM SIGSOFT Software Engineering Notes\\
 ACM SIGSOFT Software Engineering Notes\\
 ISSN: 01635848
\item
 ACM Transactions on Multimedia Computing, Communications, and Applications\\
 ACM Trans. Multimed. Comput. Comm. Appl.\\
 ISSN: 1551-6857
\item
 ACM Transactions on Software Engineering and Methodology\\
 ACM Trans. Software Eng. Meth.\\
 ISSN: 1049-331X
\item
 Advances in Computational Mathematics\\
 Adv. Comput. Math.\\
 ISSN: 1019-7168
\item
 Advances in Water Resources\\
 Adv. Water Resour.\\
 ISSN: 0309-1708
\item
 Annals of Biomedical Engineering\\
 Ann. Biomed. Eng.\\
 ISSN: 0090-6964
\item
 Applied Cognitive Psychology\\
 Appl. Cognit. Psychol.\\
 ISSN: 0888-4080
\item
 Applied Mathematics and Computation\\
 Appl. Math. Comput.\\
 ISSN: 0096-3003
\item
 Applied Mathematical Finance\\
 Appl. Math. Finance\\
 ISSN: 1350-486X
\item
 Applied Mathematical Modelling\\
 Appl. Math. Model.\\
 ISSN: 0307-904X
\item
 Applied Mechanics and Engineering\\
 Appl. Mech. Eng.\\
 ISSN: 1425-1655
\item
 Behaviour \& Information Technology\\
 Behaviour \& Information Technology\\
 ISSN: 0144-929X
\item
 Biophysical Journal\\
 Biophys. J.\\
 ISSN: 0006-3495
\item
 BIT Numerical Mathematics\\
 BIT\\
 ISSN: 0006-3835
\item
 Campus-Wide Information Systems\\
 Camput-Wide Information Systems\\
 ISSN: 1065-0741
\item
 Computers in Biology and Medicine\\
 Comput. Biol. Med.\\
 ISSN: 0010-4825
\item
 Computer Communications\\
 Comput. Comm.\\
 ISSN: 0140-3664
\item
 Computational Geosciences\\
 Comput. Geosci.\\
 ISSN: 1420-0597
\item
 Communications in Computational Physics\\
 Comput. Phys.\\
 ISSN: 1814-2406
\item
 Computers \& Mathematics with Applications\\
 Comput. Math. Appl.\\
 ISSN: 0898-1221
\item
 Computational Mechanics. Solids, Fluids, Engineered Material, Aging Infrastructure, Molecular Dynamics, Heat Transfer, Manufacturing Processes, Optimization, Fracture \& Integrity\\
 Comput. Mech.\\
 ISSN: 0178-7675
\item
 Computer Methods in Applied Mechanics and Engineering\\
 Comput. Methods Appl. Mech. Engrg\\
 ISSN: 0045-7825
\item
 Computer Methods in Biomechanics and Biomedical Engineering\\
 Comput. Meth. Biomech. Biomed. Eng.\\
 ISSN: 1025-5842
\item
 Computing in Science \& Engineering\\
 Comput. Sci. Eng.\\
 ISSN: 1521-9615
\item
 Computing and Visualization in Science\\
 Comput. Vis. Sci.\\
 ISSN: 1432-9360
\item
 Continental Shelf Research\\
 Continent. Shelf Res.\\
 ISSN: 0278-4343
\item
 Empirical Software Engineering\\
 Empir. Software Eng.\\
 ISSN: 1382-3256
\item
 Engineering Analysis with Boundary Elements\\
 Eng. Anal. Bound. Elem.\\
 ISSN: 0955-7997
\item
 Formal Aspects of Computing\\
 Formal Aspect. Comput.\\
 ISSN: 0934-5043
\item
 Future Generation Computer Systems\\
 Future Generat. Comput. Syst.\\
 ISSN: 0167-739X
\item
 Global Journal of Pure and Applied Mathematics\\
 Global J. Pure Appl. Math.\\
 ISSN: 0973-1768
\item
 IEEE/ACM Transactions on Networking\\
 IEEE/ACM Transactions on Networking\\
 ISSN: 1063-6692
\item
 IEEE Communications Letters\\
 IEEE Comm. Lett.\\
 ISSN: 1089-7798
\item
 IEEE Communications Magazine\\
 IEEE Comm. Mag.\\
 ISSN: 0163-6804
\item
 IEEE Computer Applications in Power Magazine\\
 IEEE Comput. Appl. Power Mag.\\
 ISSN: 0895-0156
\item
 IEEE Computer Architecture Letters\\
 IEEE Comput. Architect. Lett.\\
 ISSN: 1556-6056
\item
 IEEE Control Systems Magazine\\
 IEEE Control Syst. Mag.\\
 ISSN: 1066-033X
\item
 IEEE Distributed Systems Online\\
 IEEE Distr. Syst. Online\\
 ISSN: 1541-4922
\item
 IEEE Micro Magazine\\
 IEEE Micro Magazine\\
 ISSN: 0272-1732
\item
 IEEE Network: The Magazine of Global Information Exchange\\
 IEEE Netw. Mag. Global Inform. Exchange\\
 ISSN: 0890-8044
\item
 IEEE Software Magazine\\
 IEEE Software Mag.\\
 ISSN: 0740-7459
\item
 IEEE Transactions on Biomedical Engineering\\
 IEEE Trans. Biomed. Eng.\\
 ISSN: 0018-9294
\item
 IEEE Transactions on Computers\\
 IEEE Trans. Comput.\\
 ISSN: 0018-9340
\item
 IEEE Transactions on Industrial Informatics\\
 IEEE Transactions on Industrial Informatics\\
 ISSN: 1551-3203
\item
 IEEE Transactions on Parallel and Distributed Systems\\
 IEEE Trans. Parallel Distr. Syst.\\
 ISSN: 1045-9219
\item
 IEEE Transactions on Software Engineering\\
 IEEE Trans. Software Eng.\\
 ISSN: 0098-5589
\item
 IEEE Transactions on Wireless Communications\\
 IEEE Trans. Wireless Comm.\\
 ISSN: 1536-1276
\item
 IET Communications\\
 IET Communications\\
 ISSN: 1751-8628
\item
 IMA Journal of Applied Mathematics\\
 IMA J. Appl. Math.\\
 ISSN: 0272-4960
\item
 IMA Journal of Numerical Analysis\\
 IMA J. Numer. Anal.\\
 ISSN: 0272-4979
\item
 Information Processing Letters\\
 Inform. Process. Lett.\\
 ISSN: 0020-0190
\item
 Information and Software Technology\\
 Inform. Software Tech.\\
 ISSN: 0950-5849
\item
 ISA Transactions\\
 ISA Transactions\\
 ISSN: 0019-0578
\item
 International Journal of Applied Mechanics and Engineering\\
 Appl. Mech. Eng.\\
 ISSN: 1425-1655
\item
 International Journal for Computational Methods in Engineering Science and Mechanics\\
 J. Comput. Methods Eng. Sci. Mech.\\
 ISSN: 1550-2287
\item
 International Journal of Autonomous and Adaptive Communications Systems\\
 International Journal of Autonomous and Adaptive Communications Systems\\
 ISSN: 1754-8632
\item
 International Journal of Bioelectromagnetism\\
 International Journal of Bioelectromagnetism\\
 ISSN: 1456-7857
\item
 International Journal of Computational Engineering Science\\
 Int. J. Comput. Eng. Sci.\\
 ISSN: 1465-8763
\item
 International Journal of Computer Mathematics\\
 Int. J. Comput. Math.\\
 ISSN: 0020-7160
\item
 International Journal of Forecasting\\
 Int. J. Forecast\\
 ISSN: 0169-2070
\item
 International Journal of Fluid Mechanics Research\\
 Int. J. Fluid Mech. Res.\\
 ISSN: 1064-2277
\item
 International Journal of Numerical Analysis and Modeling\\
 Int. J. Numer. Anal. Model.\\
 ISSN: 1705-5105
\item
 International Journal of Nonlinear Sciences and Numerical Simulation\\
 Int. J. Nonlinear Sci. Numer. Simul.\\
 ISSN: 1565-1339
\item
 International Journal of Nonlinear Modelling in Science and Engineering\\
 Int. J. Nonlinear Model. Sci. Eng.\\
 ISSN: 1472-085X
\item
 International Journal for Numerical Methods in Engineering\\
 Int. J. Numer. Meth. Eng.\\
 ISSN: 0029-5981
\item
 International Journal for Numerical Methods in Fluids\\
 Int. J. Numer. Meth. Fluid.\\
 ISSN: 0271-2091
\item
 International Journal of Project Management\\
 Int. J. Proj. Manag.\\
 ISSN: 0263-7863
\item
 International Journal of Pure and Applied Mathematics\\
 International Journal of Pure and Applied Mathematics\\
 ISSN: 1311-8080
\item
 International Journal of Software Engineering and Knowledge Engineering\\
 Int. J. Software Eng. Knowl. Eng.\\
 ISSN: 0218-1940
\item
 Journal of Computational Acoustics\\
 J. Comput. Acoust\\
 ISSN: 0218-396X
\item
 Journal of Computational and Applied Mathematics\\
 J. Comput. Appl. Math.\\
 ISSN: 0377-0427
\item
 Journal of Computational Finance\\
 J. Comput. Finance\\
 ISSN: 1460-1559
\item
 Journal of Computational Neuroscience\\
 J. Comput. Neurosci.\\
 ISSN: 0929-5313
\item
 Journal of Computational Physics\\
 J. Comput. Phys.\\
 ISSN: 0021-9991
\item
 Journal d'Analyse Mathematique\\
 Journal d'Analyse Mathematique\\
 ISSN: 0021-7670
\item
 Journal of Geodynamics\\
 J. Geodyn.\\
 ISSN: 0264-3707
\item
 Journal of Geophysical Research (JGR)-B\\
 J. Geophys. Res. B\\
 ISSN: 0196-6936
\item
 Journal of Medical Ultrasonics\\
 Journal of Medical Ultrasonics\\
 ISSN: 1346-4523
\item
 Journal of Network and Computer Applications\\
 J. Netw. Comput. Appl.\\
 ISSN: 1084-8045
\item
 Journal of Numerical Mathematics\\
 J. Numer. Math.\\
 ISSN: 1570-2820
\item
 Journal of Object Technology\\
 J. Object Tech.\\
 ISSN: 1660-1769
\item
 Journal of Scientific Computing\\
 J. Sci. Comput.\\
 ISSN: 0885-7474
\item
 Journal of Software Maintenance and Evolution: Research and Practice\\
 J. Software Mainten. Evol. Res. Pract.\\
 ISSN: 1532-060X
\item
 Journal of Statistical Software\\
 J. Stat. Software\\
 ISSN: 1548-7660
\item
 Journal of Systems Architecture\\
 J. Syst. Architect.\\
 ISSN: 1383-7621
\item
 Journal of Systems and Software\\
 J. Syst. Software\\
 ISSN: 0164-1212
\item
 Mathematical Biosciences\\
 Math. Biosci.\\
 ISSN: 0025-5564
\item
 Mathematics of Computation\\
 Math. Comp.\\
 ISSN: 0025-5718
\item
 Mathematics and Computers in Simulation\\
 Math. Comput. Simulat.\\
 ISSN: 0378-4754
\item
 Mathematical Geology\\
 Math. Geol.\\
 ISSN: 0882-8121
\item
 Metheoritics \& Planetary Sciences\\
 Metheoritics Planet. Sci.\\
 ISSN: 1086-9379
\item
 Mobile Networks and Applications\\
 Mobile Network. Appl.\\
 ISSN: 1383-469X
\item
 Modeling, Identification and Control. A Norwegian Research Bulletin\\
 Model. Identif. Control\\
 ISSN: 0332-7353
\item
 Multi Agent and Grid Systems\\
 Multi Agent and Grid Systems\\
 ISSN: 1574-1702
\item
 Nordic Journal of Computing\\
 Nord. J. Comput.\\
 ISSN: 1236-6064
\item
 Norwegian Journal of Geography/ Norsk Geografisk Tidsskrift\\
 Norwegian Journal of Geography/ Norsk Geografisk Tidsskrift\\
 ISSN: 0029-1951
\item
 Numerical Linear Algebra with Applications\\
 Numer. Linear Algebra Appl.\\
 ISSN: 1070-5325
\item
 Numerical Methods for Partial Differential Equations. An International Journal\\
 Numer. Methods Partial Differential Equations\\
 ISSN: 0749-159X
\item
 Numerische Mathematik\\
 Numer. Math.\\
 ISSN: 0029-599X
\item
 Optics Communications\\
 Otic. Comm.\\
 ISSN: 0030-4018
\item
 Performance Evaluation\\
 Perform. Eval.\\
 ISSN: 0166-5316
\item
 Personal and Ubiquitous Computing\\
 Personal and Ubiquitous Computing\\
 ISSN: 1617-4909
\item
 Physics of the Earth and Planetary Interiors\\
 Phys. Earth Planet. In.\\
 ISSN: 0031-9201
\item
 Physical Review B: Condensed Matter and Materials Physics\\
 Phys. Rev. B Condens. Matter\\
 ISSN: 1098-0121
\item
 Proceedings / IEEE Computer Society Bioinformatics Conference. IEEE Computer Society Bioinformatics Conference\\
 Proc. IEEE Comput. Soc. Bioinformatics Conf. IEEE Comput. Soc. Bioinformatic\\
 ISSN: 1555-3930
\item
 Research Letters in Communications\\
 Research Letters in Communications\\
 ISSN: 1687-6741
\item
 Scandinavian Journal of Information Systems\\
 Scand. J. Inform. Syst.\\
 ISSN: 0905-0167
\item
 Scientific Programming\\
 Sci. Program.\\
 ISSN: 1058-9244
\item
 SIAM Journal on Numerical Analysis\\
 SIAM J. Numer. Anal.\\
 ISSN: 0036-1429
\item
 SIAM Journal on Scientific Computing\\
 SIAM J. Sci. Comput.\\
 ISSN: 1064-8275
\item
 Software Process: Improvement and Practice\\
 Software Process Improv. Pract.\\
 ISSN: 1077-4866
\item
 Software and Systems Modeling\\
 Software Syst. Model.\\
 ISSN: 1619-1366
\item
 Stroke\\
 Stroke\\
 ISSN: 0039-2499
\item
 Transactions on Machine Learning and Data Mining\\
 Transactions on Machine Learning and Data Mining\\
 ISSN: 1865-6781
\item
 Transport in Porous Media\\
 Transp. Porous Media\\
 ISSN: 0169-3913
\item
 Wireless Personal Communications\\
 Wireless Pers. Comm.\\
 ISSN: 0929-6212
\end{enumerate}